Validating FF-Replan vs.\@ a State-Of-The-Art Probabilistic Planner in Translated Real World Domains

### 2014-03-29 FinalPaper/paper.tex
more about glutton, points added to problem definition

@@

\subsubsection{Probabilistic Planning via Determinization in Hindsight (2008)~\cite{yoon2008probabilistic}}

@@

\subsubsection{Improving Determinization in Hindsight for Online Probabilistic Planning (2010)~\cite{yoon2010improving}}

Hindsight optimization has enjoyed some success for online probabilistic
planning. Although it has proven to be effective for many domains, it is
computationally expensive. This paper presents significant improvements.  1) a
method for detecting potential useful actions, 2) exploit determinism in the
domain by reusing relevant plans, 2) improves action evaluation by increasing
the chance that at least one deterministic plan reaches a goal.

\subsubsection{Probabilistic Planning in the Graphplan Framework (1999)~\cite{Blum99probabilisticplanning}}

Graphplan is a successful planning algorithm for classical STRIPS domains. This
paper explores the extend it can be used in \emph{probabilistic} domains. The
paper discusses two variations of Graphplan: PGraphplan and TGraphplan.
PGraphplan produces an optimal plan, while TGraphplan produces a sub-optimal
plan but it has increased speed. By comparing the speed and quality of the
two planners the authors are able to estimate how far they are from the ideal.

\subsubsection{Compiling Conformant Probabilistic Planning Problems into Classical Planning (2013)~\cite{taig2013conformant}}

\subsubsection{How Much Does a Household Robot Need To Know In Order To Tidy Up? (2013)~\cite{nebel2013much}}

@@

\subsubsection{Progressive heuristic search for probabilistic planning based on interaction estimates (2013)~\cite{martin2013progressive}}

@@

\subsubsection{Translation based approaches to probabilistic planning (2013)~\cite{taig2013translation}}

\subsubsection{Reverse Iterative Deepening for Finite-Horizon MDPs with Large Branching Factors (2012)~\cite{kolobov2012glutton}}
The IPPC-2011 introduces more realistic MDPs to accommodate real-world systems with large branching factors cause by \emph{natural dynamics} and a limited time for the planner to come up with a policy. For this reason planners needed to be scalable and sensitive to the expected reward maximization. Glutton introduces an off-line algorithm based on LR\textsuperscript{2}TDP and relies on the fact that a successful policy can be produced by solving an MDP M(H) for a smaller horizon h.  Incrementally solving the sequence M(1), M(2) forms the basis of LR\textsuperscript{2}TDP. By iterating on the distance from the horizon, data can be reused (and is stored in the cache until the hash-table is full). The max-reward heuristic finds the largest horizon value h' for which already a heuristic value V is estimated. The  computation time remains much lower because it runs quickly into states that converged while solving M(h-1). The max-reward computation relies on knowing the maximum reward any action can yield in any state or an upper bound on it.

%TODO still have to describe the Glutton variation on LR2TDP

\subsubsection{Probabilistic planning vs Replanning}
Inspired by the FF-Replan entrance in the IPPC competition, this paper described a probabilistic interestingness quality of domains. It then compares probabilistic planners with replanners in the different domains to draw conclusions. Classical planning with replanning upon failure when there is so little or so much uncertainty about the world that it is not worth modelling and reasoning about or when goals dynamically change or when the problem is too large to solve at once. Probabilistic planners are more appropriate when avoiding irreparable or costly failures. Probabilistic planning computes a plan that can handle all foreseeable contingencies and is preferable for quick reactions in closed control loops.

>>>>

\subsection{Planning problem}
\begin{itemize}
	\item Describe the MDP finite horizon planning problem
	\item reason about the \emph{augmented state space} of M(H), which is a set \emph{S x (0, ... , H)} of state number of steps-to-go pairs
	\item Describe reward heuristic
	\item Solving M(H) means finding a policy: a rule for selecting actions in augmented states so that executing the actions recommended by the policy starting in the initial state will accumulate the largest exected reward over H steps time
	\item The challenge or large branching factors
\end{itemize}

@@

\subsection{Probabilistic Planning via Determinization in Hindsight (2008)~\cite{yoon2008probabilistic}}

@@

\subsection{Improving Determinization in Hindsight for Online Probabilistic Planning (2010)~\cite{yoon2010improving}}
Hindsight optimization has enjoyed some success for online probabilistic
planning. Although it has proven to be effective for many domains, it is
computationally expensive. This paper presents significant improvements.  1) a
method for detecting potential useful actions, 2) exploit determinism in the
domain by reusing relevant plans, 2) improves action evaluation by increasing
the chance that at least one deterministic plan reaches a goal.

\subsection{Probabilistic Planning in the Graphplan Framework (1999)~\cite{Blum99probabilisticplanning}}
% might not be necessary?
Graphplan is a successful planning algorithm for classical STRIPS domains. This
paper explores the extend it can be used in \emph{probabilistic} domains. The
paper discusses two variations of Graphplan: PGraphplan and TGraphplan.
PGraphplan produces an optimal plan, while TGraphplan produces a sub-optimal
plan but it has increased speed. By comparing the speed and quality of the
two planners the authors are able to estimate how far they are from the ideal.

%\subsection{Compiling Conformant Probabilistic Planning Problems into Classical Planning (2013)~\cite{taig2013conformant}}
% not necessary?

\subsection{How Much Does a Household Robot Need To Know In Order To Tidy Up? (2013)~\cite{nebel2013much}}

@@

\subsection{Progressive heuristic search for probabilistic planning based on interaction estimates (2013)~\cite{martin2013progressive}}

@@

%\subsection{Translation based approaches to probabilistic planning (2013)~\cite{taig2013translation}}
% I don't think one is valuable

\subsection{Reverse Iterative Deepening for Finite-Horizon MDPs with Large Branching Factors (2012)~\cite{kolobov2012glutton}}
The IPPC-2011 introduces more realistic MDPs to accommodate real-world systems with large branching factors cause by \emph{natural dynamics} and a limited time for the planner to come up with a policy. For this reason planners needed to be scalable and sensitive to the expected reward maximization. Glutton introduces an off-line algorithm based on LR\textsuperscript{2}TDP and relies on the fact that a successful policy can be produced by solving an MDP M(H) for a smaller horizon h.  Incrementally solving the sequence M(1), M(2) forms the basis of LR\textsuperscript{2}TDP. By iterating on the distance from the horizon, data can be reused (and is stored in the cache until the hash-table is full). The max-reward heuristic finds the largest horizon value h' for which already a heuristic value V is estimated. The  computation time remains much lower because it runs quickly into states that converged while solving M(h-1). The max-reward computation relies on knowing the maximum \textsubscriptreward any action can yield in any state or an upper bound on it.

\subsubsection{LRTDP}
Using goal oriented MDPs, the \emph{Labelled Real-Time Dynamic Programmer} (LRTDP) operates a series of trials starting from s\textsubscript{0}. 
\begin{itemize}
	\item Trials start at s\textsubscript{0}
	\item Choose best action greedily in the current state based on current \emph(V)
	\item Perform  Bellman backup on the current state
	\item Sample the outcome as the chosen action
	\item Transition to the new state
	\item Repeat untill a goal, dead end or converged state is reached
	\item After trial, special convergence check on all states in the trial is performed to prove the convergence of these values
\end{itemize}

\subsubsection{LRTDP-FH}
Adapting LRTDP to a finite horizon MDP \emph{M(H)} requires to let each trial start at (\emph{s\textsubscript{0}, H}) and run for at most H time steps. A steps H steps away from s\textsubscript{0} would translate to goals in a goal-oriented MDP. However, it's anytime performance to meet the demands of a dynamic environment is not very good, creating the need for a more sophisticated approach \cite{kolobov2012glutton}.

\subsubsection{LR\textsuperscript{2}TDP}
LR\textsuperscript{2}TDP uses \emph{reverse iterative deepening} and LRTDP-FH to solve a sequence of MDPs \emph{M(1), M(2), ... , M(H)}, in that order. It first decides how to act optimally in (s\textsubscript{0}, 1), equavalent to solving M(1) , then (s\textsubscript{0}, 2), equavalent to solving M(2), eventually solvin M(H) or running out of time halting a M(h') where h' < H. This incremental effort allows for reusing state values computed in previous states, so it memorizes all vaues and solves for smaller horizons by backchaining from the goal LRTDP-FH iterates over search depth while LR\textsuperscript{2}TDP iterates over the distance from the horizon and is likely to be better because:
 \begin{itemize}
	\item In many MDPs, the optimal policy M(h) for some h < H is near optimal for M(H), it thus may have a solution when stopped prematurely
	\item it's trials are very short because backchaining from the goal leads to a lots of convergence
	\item It optimally memorizes a large fraction of augmented states to save memory
	\item a large fraction of state space may be unreachable from s\textsubscript{0} and it avoid storing information it does not need

	\item it should however use a heuristic to treat states that has never been encountered when stopped prematurely, could be a fall back or a default action.  
\end{itemize}

\subsection{Probabilistic planning vs Replanning}
Inspired by the FF-Replan entrance in the IPPC competition, this paper described a probabilistic interestingness quality of domains. It then compares probabilistic planners with replanners in the different domains to draw conclusions. Classical planning with replanning upon failure when there is so little or so much uncertainty about the world that it is not worth modelling and reasoning about or when goals dynamically change or when the problem is too large to solve at once. Probabilistic planners are more appropriate when avoiding irreparable or costly failures. Probabilistic planning computes a plan that can handle all foreseeable contingencies and is preferable for quick reactions in closed control loops.
